Verifying Spatial Properties of Stencil Computations

### 2016-11-15 paper.tex
small rearrangement

\item (\emph{overlapping}) Given two region constants $R_1$ and $R_2$ 
on the same dimension, then some combinations of region constants
can be coalesced into a single region constant $R_3$ if $R_1$ completely
overlaps $R_2$. There are five possible instantiations of the
following rule $R_1 + R_2 \equiv R_3$ which we denote: $\term{fwd + fwd} \equiv \term{fwd}$, $\term{bwd + bwd} \equiv \term{bwd}$, 
$\term{cen + cen} \equiv \term{cen}$, $\term{cen + fwd} \equiv \term{cen}$ and
$\term{cen + bwd} \equiv \term{cen}$
%
\newcommand{\stenGR}[4]{\small{\textit{#4}(\term{depth=}#1,
  \term{dim=}#2, #3)}}
\newcommand{\stenG}[3]{\small{\textit{#3}(\term{depth=}#1,
  \term{dim=}#2)}}
\begin{align*}
\hspace{-1em} & \stenGR{n}{d}{p \vee q}{$R_3$} \\[-0.4em]
\hspace{-1em} \equiv \; & \stenGR{n}{d}{p}{$R_1$} \; \texttt{+} \; \stenGR{m}{d}{q}{$R_2$}
\end{align*}
where $n \geq m$ and $p$ and $q$ range
over booleans representing the absence (true) or presence (false)
of \irrefl{} which are combined via disjunction.

>>>>

\item (\emph{overlapping}) Given two region constants $R_1$ and $R_2$ 
on the same dimension, then some combinations of region constants
can be coalesced into a single region constant $R_3$ if $R_1$ completely
overlaps $R_2$. There are five possible instantiations of the
following rule $R_1 + R_2 \equiv R_3$:
%
\newcommand{\stenGR}[4]{\small{\textit{#4}(\term{depth=}#1,
  \term{dim=}#2, #3)}}
\newcommand{\stenG}[3]{\small{\textit{#3}(\term{depth=}#1,
  \term{dim=}#2)}}
\begin{align*}
\hspace{-1em} & \stenGR{n}{d}{p \vee q}{$R_3$} \\[-0.4em]
\hspace{-1em} \equiv \; & \stenGR{n}{d}{p}{$R_1$} \; \texttt{+} \; \stenGR{m}{d}{q}{$R_2$}
\end{align*}
where $n \geq m$ and $p$ and $q$ range
over booleans representing the absence (true) or presence (false)
of \irrefl{} which are combined via disjunction.
We denote the possibilities as $\term{fwd + fwd} \equiv \term{fwd}$, $\term{bwd + bwd} \equiv \term{bwd}$, 
$\term{cen + cen} \equiv \term{cen}$, $\term{cen + fwd} \equiv \term{cen}$ and
$\term{cen + bwd} \equiv \term{cen}$.
